Plots for Latent Hawkes Paper

### 2020-07-26 output_scripts/Paper_Plots.Rmd
add plots for slides

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "paper_figure/",
                      dev = 'png', fig.height = 4.5, fig.width = 7,
                      warning = FALSE)
```

@@

```{r fig-rank-slides, fig.height=3}

@@

```{r fig_pr_slides, fig.height=3, fig.width=7}
current_cohort <- 5

@@

temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
p3 <- temp_plot_df %>%
  rowwise() %>%
  mutate(norm = min(norm,60)) %>%
  ggplot( aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 60)
p3
```

@@

```{r fig-slides-predict}
load("../output/plot_N_predict_new.RData")
temp_plot_df <- all_cohort_norm_df %>% 
  group_by(day, method) %>% 
  summarise(avg=mean(norm), n= n(), sd=sd(norm),
            se = sd/sqrt(n))

@@

```{r}

@@

temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
p4_slides <- temp_plot_df %>% #filter(method != "C-HP") %>% 
  #filter(method != "I-MMHP") %>%
  ggplot(aes(x=day, y=avg, group=method, color=method)) + 
  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
                 position=position_dodge(0.2)) +
  scale_color_manual(values = viridis::viridis(5)) + 
  #ggtitle("(b)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 18)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") + 
  coord_cartesian(ylim=c(2.5,57.5)) + 
  guides(color=guide_legend(title="Model")) #+ ylim(c(0,1000))
p4_slides

@@

@@

```{r construct data for plot, results='hide',message=FALSE,cache=FALSE}
library(PlayerRatings)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "paper_figure/",
                      dev = 'png', fig.height = 4.5, fig.width = 7,
                      warning = FALSE)

slides_plots <- TRUE
```

@@

```{r fig-rank-slides, fig.height=3,include=slides_plots,eval=slides_plots}

@@

```{r fig_pr_slides, fig.height=3, fig.width=7, include=slides_plots,eval=slides_plots}
current_cohort <- 5

@@

temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
p3 <- temp_plot_df %>%
  rowwise() %>%
  mutate(norm = min(norm,60)) %>%
  ggplot( aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 60)
p3
```
```{r fig-pred-cohort-slides, include=slides_plots,eval=slides_plots, fig.height=3}
load("../output/plot_N_predict_new.RData")
current_cohort <- 5# cohort 1 looks worse than rest
# 3 looks nice

temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
p3_slides <- temp_plot_df %>%
  filter(method != "I-MMHP") %>%
  rowwise() %>%
  mutate(norm = min(norm,120)) %>%
  ggplot( aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  #ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  #ylim(0, 60) +
  NULL
p3_slides
```

@@

```{r fig-slides-predict,include=slides_plots,eval=slides_plots,fig.height=3}
load("../output/plot_N_predict_new.RData")
temp_plot_df <- all_cohort_norm_df %>% 
  group_by(day, method) %>% 
  summarise(avg=mean(norm), n= n(), sd=sd(norm),
            se = sd/sqrt(n))

@@

```{r, include=FALSE,eval=FALSE}

@@

temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
p4_slides <- temp_plot_df %>% #filter(method != "C-HP") %>% 
  #filter(method != "I-MMHP") %>%
  ggplot(aes(x=day, y=avg, group=method, color=method)) + 
  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_errorbar(aes(ymin=max(0,avg-sd), ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
                 position=position_dodge(0.2)) +
  scale_color_manual(values = viridis::viridis(5)) + 
  #ggtitle("(b)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 18)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") + 
  #coord_cartesian(ylim=c(2.5,57.5)) + 
  guides(color=guide_legend(title="Model")) #+ ylim(c(0,1000))
p4_slides

@@

```{r fig-pred-cor, eval=slides_plots,include=slides_plots,fig.height=3}
load("../output/plot_rank_predict.RData")
current_cohort <- 5
temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),width=600,height=300)
temp_plot_df <- temp_plot_df %>%
  filter(method != "I-MMHP") 
p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  #scale_fill_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
  #ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Rank correlation") +
  ylim(0, 1)
p5
```

@@

```{r construct data for plot, results='hide',message=FALSE,cache=TRUE}
library(PlayerRatings)

@@

```{r fig-glicko-pred-slides,eval=slides_plots,include=slides_plots}
par(mar=c(3,5,3,1))
plot(1, type="n", xlab="", ylab="Glicko ranking", xlim=c(0,dim(gl$history)[2]),
     ylim=c(min(gl$history[,,1]),max(gl$history[,,1])),
     cex.axis=2, cex.lab=2)
for(m in c(1:mice_number)){
  #history
  lines(gl$history[m,1:training_end,1],
        cex=0.6, col=col_vec[m],lwd=history_width,lty=ltypes_vec[m])
  lines(c(rep(NA,training_end), gl$history[m,(training_end+1):testing_end,1]),
        cex=0.6, col=shade_vec[m],lwd=history_width,lty=ltypes_vec[m])

# annotate the days
for(d in c(19:21)){
  abline(v = nrow(df[df$day<=(d-1),]),lty=2,lwd=0.4)
  text(x=nrow(df[df$day<=(d-1),]),y=2600,d)
}
#mtext(text="(a)", side=3, line=-2.3, outer=TRUE, cex=2.8, at=0.5, font=2)
```
